A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
added footnote

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term. Here, a conjunctive term is visited
iff its atomic subterms are visited, and zero or one of its immediate
probabilistic subterms are visited. For a sequential session, the
starting state corresponds to an assumption (usually unique) with
probability $1$. In our example, that starting state is:

@@

\noindent Taking the switching action \switchAction\ to be
$(\pp{look}~\pp{box}~\pp{office})$, we have that
$\actions^{\circ}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}))$ is not
relevant for this session, and therefore exclude it from the
abstract decision process.

Given \switchAction, we also include another once-only self-transition
action $\actions.\poss(\switchAction)$, the \emph{confirmation action}
with the reward property:

>>>>

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term. Here, a conjunctive term is
visited iff its atomic subterms are visited, and zero or one of its
immediate probabilistic subterms are visited. For a sequential
session, the starting state corresponds to an assumption (usually
unique) with probability $1$.\footnote{To simplify the discussion, we
suppose that conjunctive terms include all atoms that are true with
probability 1 according to their visitation.} In our example, that starting state is:

\vspace{-1ex}

@@

\noindent Taking the switching action \switchAction\ to be
$(\pp{look}~\pp{box}~\pp{office})$, we have that
$\actions^{\circ}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}))$ is not
relevant for this session, and therefore we exclude the corresponding
disconfirm action from the abstract decision process.

Given \switchAction, we also include another once-only self-transition
action $\actions.\poss(\switchAction)$, a \emph{confirmation action}
with the reward property:
